Blocks of extended ancestry around selected loci in hybrid zones

### 2016-02-28 drafts/hybrid_zone.tex

>>>>

\plr{note that when drift starts to kick in for clines (around $\tau=320$) we start to get better power with haplotype lengths}

\plr{This first paragraph sounds like the Introduction.  A brief recap here is good: maybe something like:
    Our goal in this paper was to describe cline formation and haplotype structure around a new hybrid zone,
    which we have done using both theory and simulation.
    Our most useful observations are that clines establish over time $1/s$,
    and that lineages of selected loci found on the side of the hybrid zone where they are at a disadvantage
    tend to move back towards the side where they are common
    at speed $\sigma/\sqrt{s}$.
    This predicts that blocks of ancestry are longer near the center, flanked by shorter ones ...
}

### 2016-02-28 drafts/supplement.tex

>>>>

\begin{figure}
    \includegraphics{figs/cond_freqs_comparison_tau_80}
    \caption{
        \textbf{Conditional frequencies of ancestry $A$ at $\tau=80$},
        comparing simulation and theory, with $\sigma=3$ deme spacings, $s=0.05$, and 50 individuals per deme.
        The top left figure shows observed and expected genotype frequencies for the two homozygotes and the heterozygote at the selected locus;
        expected genotype counts were obtained assuming random mating,
        and by solving equation \eqref{eqn:cline_pde} numerically.
        The remaining figures show observed and expected frequencies of $A$ ancestry,
        separately conditioned on the identity of the linked allele at the selected site.
        Observed frequencies become much noisier where the linked allele becomes rarer.
    } \label{sfig:condAlleleFreq_tau80_comparison}
\end{figure}

\begin{figure}
    \includegraphics{figs/cond_freqs_comparison_tau_320}
    \caption{
        \textbf{Conditional frequencies of ancestry $A$ at $\tau=320$},
        as in figure \ref{sfig:condAlleleFreq_tau80_comparison}.
        Deviations are larger than at $\tau=80$, 
        due to genetic drift.
    } \label{sfig:condAlleleFreq_tau320_comparison}
\end{figure}

\begin{figure}
    \includegraphics{figs/cond_freqs_comparison_tau_1280}
    \caption{
        \textbf{Conditional frequencies of ancestry $A$ at $\tau=1280$},
        as in figure \ref{sfig:condAlleleFreq_tau80_comparison}.
        Deviations are larger still than at $\tau=320$, 
        due to genetic drift.
    } \label{sfig:condAlleleFreq_tau1280_comparison}
\end{figure}
